\begin{itemize}
\item[]
Thank you my advisor, Dr. Wojciech Matusik, for your support, innovative ideas and commitment to research on computational fabrication and physics-based simulation.
\item[]
Thank you my thesis readers, Dr. Justin Solomon and Dr. Markus J. Buehler for providing valuable feedback to this thesis using your expertise.
\item[]
Thank you Dr. David I. W. Levin for introducing me to the wonderful world of FEM simulation and for providing advise throughout my PhD study.
\item[]
Thank you Dr. Shinjiro Sueda for your help on data-driven FEM.
\item[]
Thank you Dr. Danny Kaufman for your knowledge on dynamics simulation and for advocating our project on designing dynamic mechanisms.
\item[]
Thank you Dr. Bo Zhu and Dr. M\'{e}lina Skouras for your knowledge and hard work on topology optimization and fast numerical solvers.
\item[]
Thank you Dr. Pitchaya Sitthi-Amorn and Dr. Piotr Didyk for your help on designing 3D prints.
\item[]
Thank you Dr. James Thompkin and Dan Ramirez for your assistance to paper production.
\item[]
Thank you lab members of the Computational Fabrication Group: Vahid Babaei, Britton Mae Bradley, Tao du, Alexandre Kaspar, Hui Qiao, Adriana 
Schulz, Maria Shugrina, Andrew Spielberg, and many others for helping me and for being good company.
\item[]
Thank you Dr. Etienne Vouga, Dr. Uri Ascher and Dr. Eitan Grinspun for insightful comments and suggestions.
\item[]
Thank you Gaurav Bharaj, Tzu-Mao Li and Lukas Murmann for user study assistance.
\item[]
Thank you Jiaqi Xing, my dear wife, for your support and understanding throughout the years.
\end{itemize}
